---
title: "Exploratory Data Analysis on COVID-19 Data on Kaggle"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    source_code: "https://github.com/silasbea/covid-19-explore"
---

```{r setup, include=FALSE}
library(flexdashboard)
library(dplyr)
library(tidyr)
library(readr)

data <- read_csv('/home/silas/https:/github.com/silasbea/covid-19-explore/covid-deaths.csv')

data %>% 
  filter(location != 'World' & location != 'High income' & location != 'Upper middle income' & location != 'Europe' & location != 'Asia' & location != 'Africa' & location != 'North America' & location != 'South America' & location != 'Lower middle income' & location != 'European Union' & location != 'Low income') %>%
  select(location, population, continent, total_deaths, total_cases, icu_patients, new_deaths_smoothed) %>% 
  arrange(desc(total_deaths))  -> messy_countries
   
messy_countries %>% 
  group_by(location) %>% 
  summarise(across(everything(), first)) -> countries


```
# Home
## Column {data-width="600" .tabset}

### COVID deaths by countries

```{r}
library(dplyr)
library(ggplot2)
library(plotly)

countries %>% 
  filter(total_deaths > 94000) %>% 
  ggplot(mapping = aes(x = total_deaths, y = location, color = continent, shape = continent)) +
  geom_point(size = 3) +
  theme_minimal() +
  labs(
    x = "Total Human Deaths",
    y = 'Countries'
  )-> plot

ggplotly(plot)

```

### Total cases by location

```{r}
library(dplyr)
library(ggplot2)
library(plotly)

countries %>% 
  filter(total_deaths > 94000) %>% 
  ggplot(mapping = aes(x = total_cases, y = location, color = continent, shape = continent)) +
  geom_point(size = 3) +
  theme_minimal() +
  labs(
    x = "COVID-19 Cases per country",
    y = 'Countries'
  )-> plot

ggplotly(plot)
```


## Column {data-width="600" .tabset}

### New deaths by Continent

```{r}
library(dplyr)
library(ggplot2)
library(plotly)

countries %>% 
  filter(total_deaths > 94000) %>% 
  ggplot(mapping = aes(x = new_deaths_smoothed, y = continent, color = continent)) +
  geom_line(size = 2) +
  #theme_classic() +
  labs(
    x = "New Death Cases",
    y = 'Continents'
  )-> plot

ggplotly(plot)
```

### Distribution by Boxplot

```{r}
library(dplyr)
library(ggplot2)

countries %>% 
  filter(total_deaths > 94000) %>% 
  ggplot(mapping = aes(x = new_deaths_smoothed, y = continent, fill = continent)) +
  geom_boxplot() +
  #theme_classic() +
  labs(
    x = "New Death Cases",
    y = 'Continents'
  )-> plot

plot
```


# About the Dataset
This EDA, assumptions and inferences are drawn from the Covid-19 deaths and vaccinations Dataset on
Kaggle.com. The Covid-19 deaths dataset contains data including total deaths and new deaths, across different
locations and time periods. 

By exploring and analyzing this data, we uncover insights into the global impact of
Covid-19 and explore the relationship between locations, continents and deaths resulting. 

This dataset is a
valuable resource for researchers, data analysts, and anyone interested in understanding the ongoing pandemic.